---
title: "eARThKids survey report - April 2018"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, include = TRUE, fig.width = 8)

library(tidyverse)
library(googlesheets)
library(janitor)
library(scales)
library(htmlwidgets)
library(knitr)
library(kableExtra)
library(bookdown)


source("https://raw.githubusercontent.com/dgkeyes/dk-functions-and-themes/master/themes/mna_themes.R")
source("https://raw.githubusercontent.com/dgkeyes/dk-functions-and-themes/master/functions/dk_functions.R")


```

```{r get_data, include=FALSE}

# GET DATA ----------------------------------------------------------------

earthkids.surveys.artists.sheet <- gs_title("eARThKids Teaching Artist Survey (Responses)")

earthkids.surveys.artists.data <- gs_read(earthkids.surveys.artists.sheet)


earthkids.surveys.teachers.sheet <- gs_title("eARThKids Teacher Survey (Responses)")

earthkids.surveys.teachers.data <- gs_read(earthkids.surveys.teachers.sheet) 


# CREATE SUBSETS OF DATA --------------------------------------------------

satisfaction.questions <- c("I feel confident that I understand what arts integration is",
                            "I feel confident delivering arts-integrated instruction",
                            "Arts integration is a useful strategy for teaching students with diverse learning styles",
                            "Arts integration can help teachers be more effective as educators",
                            "I am confident that I can now integrate arts into my daily lesson(s) than I did before",
                            "Through participation in the eARThKids program, I have learned the value of collaborating with a teaching artist/teacher",
                            "Through participation in the eARThKids program, I have improved my ability to co-teach an arts-integrated lesson",
                            "After the program, I feel that the my students are showing growth (or change) in their reading (habits and understanding)",
                            "After the program, I feel that the students have a better understanding of the environment around them",
                            "The eARThKids program was engaging for the students",
                            "Aspects of the eARThKids program have had an impact on students’ critical thinking skills",
                            "Students have demonstrated higher levels of involvement in the learning process",
                            "Students demonstrated their own initiative and creativity through their participation in the various activities",
                            "The Growing UP Green/eARThKids curriculum is aligned well with grade 1 ELA, fine arts and science standards and indicators",
                            "Using lessons from the Growing Up Green/eARThKids curriculum to teach R/ELA is an effective way to improve reading abilities of my students",
                            "Lesson plan activity was useful to me",
                            "I co-planned the lessons with the teaching artist/teacher")

earthkids.surveys.artists.satisfaction <- earthkids.surveys.artists.data %>%
     select(contains("Based on your experience")) %>%
     set_names(satisfaction.questions) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(respondent = "Teachers")

earthkids.surveys.teachers.satisfaction <- earthkids.surveys.teachers.data %>%
     select(contains("Based on your experience")) %>%
     set_names(satisfaction.questions) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(respondent = "Artists")


earthkids.satisfaction <- bind_rows(earthkids.surveys.artists.satisfaction, earthkids.surveys.teachers.satisfaction) %>%
     group_by(respondent, question) %>%
     count(response) %>%
     filter(response != "Neither Agree nor Disagree") %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(n_inv = ifelse(response == "Disagree", n * -1, n)) %>%
     mutate(pct_inv = ifelse(response == "Disagree", pct * -1, pct)) %>%
     ungroup() %>%
     # mutate(question = str_wrap(question, width = 40)) %>%
     mutate(response = fct_relevel(response, c("Strongly Agree",
                                               "Agree",
                                               "Disagree")))




```

# Introduction




The external evaluation of eARThKids by MN Associates, Inc. examines to what extent the various strategies and activities of the project have led to the intended programmatic outcomes. The main sources of data collection are: document reviews, meeting notes, teacher and teaching artists surveys, students' demographics and attendance data, and pre-and-post student assessments using data from the Directed Reading Assessments.

The eARThKids evaluation is based on the following evaluation questions:

<b>Program Implementation</b>

1. To what extent are the participating schools implementing the eARThKids model as designed and envisioned by the Young Audiences and PG County Public Schools?

2. To what extent do participating teachers find eARThKids to be effective in (a) successfully improving their instructional practices through co-teaching and professional development?

<b>Program Impact</b>

1. To what extent has the eARThKids out-of-school-time program assisted students in meeting academic requirements on grade level?

This short survey summary report was generated from data collected from the classroom teachers and teaching artists for the eARThKids program has been completed by MN Associates, Inc.  

# Overall Satisfaction

Question asked: Based on your experience as a classroom teacher/teaching artist in the eARThKids program, please rate the degree to which you agree to the following statements that speak to your knowledge and satisfaction with the program:

<div align="center">
<span style="color: #F05356; font-weight: 700;">Disagree</span>&nbsp;&nbsp;
<span style="color: #BFD958; font-weight: 700;">Agree</span>&nbsp;&nbsp;
<span style="color: #2BAADF; font-weight: 700;">Strongly agree</span>
</div>

```{r satisfaction, echo = FALSE, fig.height = 15}

ggplot(earthkids.satisfaction, aes(x = respondent, y = n_inv,
                                   fill = factor(response))) +    
     geom_bar(stat = "identity", position = "stack") +
     geom_text(aes(label = n),
               position = position_stack(vjust = .5),
               color = "white") +
     coord_flip() +
     facet_wrap(~question, ncol = 2, labeller=label_wrap_gen(width=35)) +
     scale_fill_manual(values = c(mna.blue, mna.green, mna.red)) +
     mna.bar.chart.theme + 
     theme(axis.text.x = element_blank(),
           panel.grid.major.x = element_blank())

```

# Learning

Question asked to teaching artists: I feel that the teacher(s) I worked with can... 
<br>
Question asked to teachers: I can... 

<div align="center">
<span style="color: #F05356; font-weight: 700;">Disagree</span>&nbsp;&nbsp;
<span style="color: #BFD958; font-weight: 700;">Agree</span>&nbsp;&nbsp;
<span style="color: #2BAADF; font-weight: 700;">Strongly agree</span>
</div>

```{r teacher_qualities, echo = FALSE, fig.height = 8}


qualities.questions <- c("Design an arts-integrated lesson",
                         "Identify learner outcomes in an arts-integrated lesson",
                         "Connect the Common Core Standards with Arts Standards",
                         "Collaborate and plan without a teaching artist",
                         "Help students develop 21st century skills through the integration of the arts in my lessons",
                         "Use the arts to connect with students’ prior knowledge",
                         "Assess an arts-integrated lesson")

earthkids.teacher.qualities.teachers <- earthkids.surveys.teachers.data %>%
     select(contains("I can...")) %>%
     set_names(qualities.questions) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(respondent = "Artists")

earthkids.artists.qualities.teachers <- earthkids.surveys.artists.data %>%
     select(contains("I feel that the teacher")) %>%
     set_names(qualities.questions) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(respondent = "Teachers")


teacher.qualities <- bind_rows(earthkids.artists.qualities.teachers, earthkids.teacher.qualities.teachers) %>%
     group_by(respondent, question) %>%
     count(response) %>%
     filter(response != "Neither Agree nor Disagree") %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(n_inv = ifelse(response == "Disagree", n * -1, n)) %>%
     mutate(pct_inv = ifelse(response == "Disagree", pct * -1, pct)) %>%
     ungroup() %>%
     mutate(response = str_wrap(response, width = 40)) %>%
     mutate(response = fct_relevel(response, c("Strongly Agree",
                                               "Agree")))

ggplot(teacher.qualities, aes(x = respondent, y = n_inv,
                              fill = factor(response))) +    
     geom_bar(stat = "identity", position = "stack") +
     geom_text(aes(label = n),
               position = position_stack(vjust = .5),
               color = "white") +
     coord_flip() +
     facet_wrap(~question, ncol = 2, labeller=label_wrap_gen(width=35)) +
     scale_fill_manual(values = c(mna.blue, mna.green, mna.red)) +
     mna.bar.chart.theme + 
     theme(axis.text.x = element_blank(),
           panel.grid.major.x = element_blank())
```

# Professional Development

<div align="center">
<span style="color: #F05356; font-weight: 700;">Disagree</span>&nbsp;&nbsp;
<span style="color: #BFD958; font-weight: 700;">Agree</span>&nbsp;&nbsp;
<span style="color: #2BAADF; font-weight: 700;">Strongly agree</span>
</div>

```{r pd, echo = FALSE, fig.height = 8}

dk_delete_mna_extras <- function(item) {
     item <- str_replace(item, "\\[", "")
     item <- str_replace(item, "\\]", "")
     item <- str_replace(item, "\\.", "")
}

pd.teachers <- earthkids.surveys.teachers.data %>%
     select(contains("Quality of Professional")) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(question = str_replace(question,
                                   "Quality of Professional Development, Feedback, and Support ",
                                   "")) %>%
     mutate(question = dk_delete_mna_extras(question)) %>%
     mutate(question = str_replace(question,
                                   "Opportunities to collaborate with the teaching artist was sufficient",
                                   "Opportunities to collaborate with teaching artists were sufficient")) %>%
     mutate(question = str_replace(question,
                                   "Quality of feedback on lessons or any other aspect from the teaching artist was high",
                                   "Quality of feedback on lessons or any other aspect from the teaching artist/teacher was high")) %>%
     mutate(respondent = "Teachers")

pd.artists <- earthkids.surveys.artists.data %>%
     select(contains("Quality of Professional")) %>%
     gather() %>%
     set_names(c("question", "response")) %>%
     mutate(question = str_replace(question,
                                   "Quality of Professional Development, Feedback, and Support ",
                                   "")) %>%
     mutate(question = dk_delete_mna_extras(question)) %>%
     mutate(question = str_replace(question,
                                   "Opportunities to collaborate with another teaching artist was sufficient",
                                   "Opportunities to collaborate with teaching artists were sufficient")) %>%
     mutate(question = str_replace(question,
                                   "Quality of feedback on lessons or any other aspect from the teacher was high",
                                   "Quality of feedback on lessons or any other aspect from the teaching artist/teacher was high")) %>%
     mutate(respondent = "Artists")

pd <- bind_rows(pd.artists, pd.teachers) %>%
     group_by(respondent, question) %>%
     count(response) %>%
     filter(response != "Neither Agree nor Disagree") %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(n_inv = ifelse(response == "Disagree", n * -1, n)) %>%
     mutate(pct_inv = ifelse(response == "Disagree", pct * -1, pct)) %>%
     ungroup() %>%
     mutate(response = str_wrap(response, width = 40)) %>%
     mutate(response = fct_relevel(response, c("Strongly Agree",
                                               "Agree")))

ggplot(pd, aes(x = respondent, y = n_inv,
               fill = factor(response))) +    
     geom_bar(stat = "identity", position = "stack") +
     geom_text(aes(label = n),
               position = position_stack(vjust = .5),
               color = "white") +
     coord_flip() +
     facet_wrap(~question, ncol = 2, labeller=label_wrap_gen(width=35)) +
     scale_fill_manual(values = c(mna.blue, mna.green, mna.red)) +
     scale_y_continuous(labels = percent) +
     mna.bar.chart.theme + 
     theme(axis.text.x = element_blank(),
           panel.grid.major.x = element_blank())
```




# Open-Ended Responses (Teaching Artists)

```{r dk_summarize_open_ended, echo = FALSE}

dk_summarize_open_ended <- function(df) {
df %>%
     set_names("response") %>%
     filter(!is.na(response)) %>%
     mutate(response = str_trim(response)) %>%
     filter(!str_detect(response, fixed("n/a", ignore_case = TRUE))) %>%
     filter(!str_detect(response, fixed("No", ignore_case = TRUE))) %>%
     filter(!str_detect(response, fixed("None", ignore_case = TRUE))) %>%
     filter(!str_detect(response, fixed("Not sure", ignore_case = TRUE))) %>%
     kable("html", col.names = colnames(df)) %>%
     kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}
```

```{r artists_responses, echo = FALSE, include = TRUE}

dk_summarize_open_ended(earthkids.surveys.artists.data[39])
dk_summarize_open_ended(earthkids.surveys.artists.data[40])
dk_summarize_open_ended(earthkids.surveys.artists.data[41])
dk_summarize_open_ended(earthkids.surveys.artists.data[42])
dk_summarize_open_ended(earthkids.surveys.artists.data[44])
dk_summarize_open_ended(earthkids.surveys.artists.data[45])

```

# Open-Ended Responses (Teachers)

```{r teachers_responses, echo = FALSE, include = TRUE}

dk_summarize_open_ended(earthkids.surveys.teachers.data[40])
dk_summarize_open_ended(earthkids.surveys.teachers.data[41])
dk_summarize_open_ended(earthkids.surveys.teachers.data[42])
dk_summarize_open_ended(earthkids.surveys.teachers.data[43])
dk_summarize_open_ended(earthkids.surveys.teachers.data[44])
dk_summarize_open_ended(earthkids.surveys.teachers.data[45])
dk_summarize_open_ended(earthkids.surveys.teachers.data[46])

```




```{r bookdown, eval = FALSE, echo = FALSE, include = FALSE}

gitbook(split_by = "chapter")
render_book("earthkids-surveys-spring-2018.Rmd", "bookdown::gitbook", output_dir = "bookdown")

```
